---
title: "Visual Analysis Two-Factor Interaction Study"
author: "Michael A. Seaman"
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: inline
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
library(tidyverse)
library(MASS)
library(gridExtra)
```

In this document we will look at the interaction among all pairs of factors that may influence agreement. It is possible to analyze additional higher-order interactions, but these will become incredibly difficult to interpret, so I am sticking to two-factor interactions here. In all cases the response variable is the agreement of experts.

```{r echo=TRUE, message=FALSE, warning=FALSE}

# Read in the data

VA <- read_csv(here("Data", "VAStudyData.csv"),
               col_types = list(
                 Graph = col_factor(),
                 True = col_factor(),
                 ExpertA = col_integer(),
                 ExpertB = col_integer(),
                 ExpertC = col_integer(),
                 ExpertD = col_integer(),
                 ExpertE = col_integer(),
                 CDC = col_factor(),
                 MachineL = col_factor(),
                 Autocorrelation = col_factor(),
                 Trend = col_factor(),
                 Variability = col_factor(),
                 PointsA = col_factor(),
                 PointsB = col_factor(),
                 EffectSize = col_integer()))

# Create an agreement variable that ranges from 3 to 5.

VA$Agree <- VA$ExpertA + VA$ExpertB + VA$ExpertC + VA$ExpertD + VA$ExpertE
VA$Agree <- ifelse(VA$Agree > 2, VA$Agree, (5 - VA$Agree))

# Recode factors

VA <- VA %>%
  mutate(True = fct_recode(True, "No" = "0", "Yes" = "1")) %>%
  mutate(True = relevel(True, "No")) %>%
  mutate(Agree = factor(Agree,
                        levels = c(3, 4, 5),
                        labels = c("No", "Yes", "Yes")))

VA <- VA %>%
  mutate(Trend = relevel(Trend, "30"))

VA <- VA %>%
  mutate(ES_Factor = factor(EffectSize))

VA <- VA %>%
  mutate(ES_Factor = fct_collapse(ES_Factor,
                                  moderate = c("1", "2", "3"),
                                  none_high = c("0", "4", "5")))
  
VA <- VA %>%
  mutate(ES_Factor = relevel(ES_Factor, "moderate"))

```

### The interaction of autocorrelation and trend

First we will look at whether *autocorrelation* and *trend* interact when influencing expert agreement.

```{r}

model_auto_trend <- glm(Agree ~ Autocorrelation * Trend,
                        family = binomial(link = "logit"),
                        data = VA)

summary(model_auto_trend)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_trend),
          confint.default(model_auto_trend, level = 0.95)))

```

Let's work through the interaction "by hand" for this first interaction to help clarify what this is telling us. First I'm going to look at the odds ratio comparing the inclusion of a trend to no trend when there is no autocorrelation.

Let's look at the odds of agreement when there is no trend and no autocorrelation.

```{r}

no_auto <- VA %>%
  filter(Autocorrelation == "0")

no_auto_no_trend <- no_auto %>%
  filter(Trend == "0") %>%
  summarize(Agree_Yes = sum(Agree == "Yes") / n(),
            Agree_No = sum(Agree == "No") / n())
  
no_auto_no_trend %>%
  summarize(Agree_Yes / Agree_No)

```

Now let's look at the odds of agreement when there is a trend and no autocorrelation.

```{r}

no_auto <- VA %>%
  filter(Autocorrelation == "0")

no_auto_trend <- no_auto %>%
  filter(Trend == "30") %>%
  summarize(Agree_Yes = sum(Agree == "Yes") / n(),
            Agree_No = sum(Agree == "No") / n())
  
no_auto_trend %>%
  summarize(Agree_Yes / Agree_No)

```

Let's do this all again, but this time with an autocorrelation.

Let's look at the odds of agreement when there is no trend but there is autocorrelation.

```{r}

auto <- VA %>%
  filter(Autocorrelation == "0.2")

auto_no_trend <- auto %>%
  filter(Trend == "0") %>%
  summarize(Agree_Yes = sum(Agree == "Yes") / n(),
            Agree_No = sum(Agree == "No") / n())
  
auto_no_trend %>%
  summarize(Agree_Yes / Agree_No)

```

Now let's look at the odds of agreement when there is a trend and there is autocorrelation.

```{r}

auto <- VA %>%
  filter(Autocorrelation == "0.2")

auto_trend <- auto %>%
  filter(Trend == "30") %>%
  summarize(Agree_Yes = sum(Agree == "Yes") / n(),
            Agree_No = sum(Agree == "No") / n())
  
auto_trend %>%
  summarize(Agree_Yes / Agree_No)

```

Now let's put it all together, starting with this last value of 2.28, which states that the odds of agreement when there is both an autocorrelation and a trend is 2.28. These are the odds for the intercept in our model and serve as a baseline to compare for our odds ratios.

Now let's look at the odds of agreement for no autocorrelation with trend and the odds of agreement for autocorrelation with trend. We have calculated these above, so now we can put these in an odds ratio.

```{r}

odds_no_auto_trend <- no_auto_trend %>%
  summarize(Agree_Yes / Agree_No)

odds_auto_trend <- auto_trend %>%
  summarize(Agree_Yes / Agree_No)

odds_no_auto_trend / odds_auto_trend

```

Note that this is the odd ratio we obtained above for no autocorrelation to autocorrelation, but now we see that this is obtained by holding the trend constant at trend.

What if we hold the trend constant at no trend and calculate the same ratio for no autocorrelation to autocorrelation?

```{r}

odds_no_auto_no_trend <- no_auto_no_trend %>%
  summarize(Agree_Yes / Agree_No)

odds_auto_no_trend <- auto_no_trend %>%
  summarize(Agree_Yes / Agree_No)

odds_no_auto_no_trend / odds_auto_no_trend

```

This does not appear to be in our odds ratio table above, but wait! Let's take the log of the odds ratio of the odds ratio.

```{r}

log((odds_no_auto_no_trend / odds_auto_no_trend) / (odds_no_auto_trend / odds_auto_trend))

```

Notice that this is the estimate of the parameter for the interaction in our model. To be able to interpret, we will exponentiate.

```{r}

exp(log((odds_no_auto_no_trend / odds_auto_no_trend) / (odds_no_auto_trend / odds_auto_trend)))

```

Ah ha! This is listed above as the odds ratio for the interaction! What does it tell us? The odds of agreement increase slightly when we remove autocorrelation. This is true whether or not there is a trend. What we find, however, is that the increase is smaller when there is no trend than when there is a trend. So this is an indication of how the presence (or lack of presence) of trend can influence the effect of autocorrelation on agreement. In this case, specifically, the effect of autocorrelation on agreement is small with a trend and even smaller without a trend, but not much. Trend has little influence on how autocorrelation influences agreement.

We have 15 of these to do. Even though we are not going to do it by hand each time, it is going to take a good deal of work and thought to interpret each one. So I decided to write a function that will do much of the work for us.

```{r}
source(here("Functions", "all_odds.R"))
```

Here's an example of the output for what we just did by hand, but even more complete. With this output, we can choose either variable as the potential moderator and describe the effects in detail. If we want to change the order of any of these, all we have to do is run another model and then use the all_odds function again. Alternatively, you can simply take the reciprocal of the interaction odds ratios.

```{r}
all_odds(model_auto_trend)
```

To express this interaction ratio as a positive, we can take the reciprocal.

```{r}
1/0.86
```

This tells us that the effect of removing the trend is more pronounced when there is an autocorrelation than when there is no autocorrelation, though this value suggests a very small interaction (16% increase) that does not lead to an inference (p = 0.63).

### The interaction of autocorrelation and variability

Next we will look at whether *autocorrelation* and *variability* interact when influencing expert agreement.

```{r}

model_auto_var <- glm(Agree ~ Autocorrelation * Variability,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_var)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_var),
          confint.default(model_auto_var, level = 0.95)))

```

```{r}
all_odds(model_auto_var)
```

A change in the variability of the points does not make much difference in the odds ratio for autocorrelation.

### The interaction of autocorrelation and number of points in Phase A

Next we will look at whether *autocorrelation* and *number of points in Phase A* interact when influencing expert agreement.

```{r}

model_auto_A <- glm(Agree ~ Autocorrelation * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_A),
          confint.default(model_auto_A, level = 0.95)))

```

```{r}
all_odds(model_auto_A)
```

A change in the number of the points in Phase A does not make much difference in the odds ratio for autocorrelation.

### The interaction of autocorrelation and number of points in Phase B

Next we will look at whether *autocorrelation* and *number of points in Phase B* interact when influencing expert agreement.

```{r}

model_auto_B <- glm(Agree ~ Autocorrelation * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_B),
          confint.default(model_auto_B, level = 0.95)))

```

```{r}
all_odds(model_auto_B)
```

A change in the number of points in Phase B does not make much difference in the odds ratio for autocorrelation.

### The interaction of autocorrelation and effect size

Next we will look at whether *autocorrelation* and *effect size* interact when influencing expert agreement.

```{r}

model_auto_effect <- glm(Agree ~ Autocorrelation * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_effect)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_effect),
          confint.default(model_auto_effect, level = 0.95)))

```


```{r}
all_odds(model_auto_effect)
```

A change in the effect size does make some difference in the odds ratio for autocorrelation, with high effect size resulting in a greater odds ratio for autocorrelation than with a moderate effect size. The p value suggests this is not a stable enough result to make a conclusion with confidence.

### The interaction of trend and variability

Next we will look at whether *trend* and *variability* interact when influencing expert agreement.

```{r}

model_trend_var <- glm(Agree ~ Trend * Variability,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_var)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_var),
          confint.default(model_trend_var, level = 0.95)))

```


```{r}
all_odds(model_trend_var)
```

A change in the variability of the points makes no difference in the odds ratio for trend.

### The interaction of trend and number of points in Phase A

Next we will look at whether *trend* and *number of points in Phase A* interact when influencing expert agreement.

```{r}

model_trend_A <- glm(Agree ~ Trend * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_A),
          confint.default(model_trend_A, level = 0.95)))

```


```{r}
all_odds(model_trend_A)
```

A change in the number of points in Phase A does not make much difference in the odds ratio for trend.

### The interaction of trend and number of points in Phase B

Next we will look at whether *trend* and *number of points in Phase B* interact when influencing expert agreement.

```{r}

model_trend_B <- glm(Agree ~ Trend * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_B),
          confint.default(model_trend_B, level = 0.95)))

```


```{r}
all_odds(model_trend_B)
```

A change in the number of points in Phase B does not make a difference in the odds ratio for trend.

### The interaction of trend and effect size

Next we will look at whether *trend* and *effect size* interact when influencing expert agreement.

```{r}

model_trend_es <- glm(Agree ~ Trend * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_es),
          confint.default(model_trend_es, level = 0.95)))

```


```{r}
all_odds(model_trend_es)
```

The odds ratio for trend is higher when the effect size is high than when it is moderate, reflecting some interaction, yet the p value indicates instability in this estimate so that we cannot put much confidence in it.

### The interaction of variability and number of points in Phase A

Next we will look at whether *variability* and *number of points in Phase A* interact when influencing expert agreement.

```{r}

model_var_A <- glm(Agree ~ Variability * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_A),
          confint.default(model_var_A, level = 0.95)))

```


```{r}
all_odds(model_var_A)
```

The odds ratio for variability is higher when there five points instead of three points in Phase A, reflecting some interaction, yet the p value indicates instability in this estimate so that we cannot be highly confident of this estimate.

### The interaction of variability and number of points in Phase B

Next we will look at whether *variability* and the *number of points in Phase B* interact when influencing expert agreement.

```{r}

model_var_B <- glm(Agree ~ Variability * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_B),
          confint.default(model_var_B, level = 0.95)))

```


```{r}
all_odds(model_var_B)
```

A change in the number of points in Phase B does not make much difference in the odds ratio for variability.

### The interaction of variability and effect size

Next we will look at whether *variability* and *effect size* interact when influencing expert agreement.

```{r}

model_var_es <- glm(Agree ~ Variability * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_es),
          confint.default(model_var_es, level = 0.95)))

```


```{r}
all_odds(model_var_es)
```

A change in the effect size does not make much difference in the odds ratio for variability.

### The interaction of number of points in Phase A and number of points in Phase B

Next we will look at whether the *number of points in Phase A* and the *number of points in Phase B* interact when influencing expert agreement.

```{r}

model_A_B <- glm(Agree ~ PointsA * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_A_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_A_B),
          confint.default(model_A_B, level = 0.95)))

```


```{r}
all_odds(model_A_B)
```

The odds ratio for the number of points in Phase A is a little higher when there are five points in Phase B than when there are ten points in Phase B, but this estimate is not stable enough to infer these results with high confidence.

### The interaction of number of points in Phase A and effect size

Next we will look at whether the *number of points in Phase A* and *effect size* interact when influencing expert agreement.

```{r}

model_A_es <- glm(Agree ~ PointsA * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_A_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_A_es),
          confint.default(model_A_es, level = 0.95)))

```


```{r}
all_odds(model_A_es)
```

A change in the effect size does not make much difference in the odds ratio for the number of points in Phase A.

### The interaction of number of points in Phase B and effect size

Next we will look at whether the *number of points in Phase B* and *effect size* interact when influencing expert agreement.

```{r}

model_B_es <- glm(Agree ~ PointsB * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_B_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_B_es),
          confint.default(model_B_es, level = 0.95)))

```


```{r}
all_odds(model_B_es)
```

A change in the effect size does not make much difference in the odds ratio for the number of points in Phase B.

## Forest plot for trend interaction

In studying individual effects of data characteristics, we note that trend and effect size had the most stable influence on agreement. Removing trend rotation increased agreement. No effects and large effects also increased agreement, when compared to moderate effects. Given our focus on these two data characteristics, let's determine if these effects remain regardless of the levels of other individual characteristics, or if it might be the case that the effect is moderated by one of these characteristics. First, we will look at the trend effect. Again, I have chosen the direction of the ratio of the odds ratios to yield positive results for comparison purposes.

First, here is autocorrelation with trend, flipping autocorrelation.

```{r}
VA <- VA %>%
  mutate(Autocorrelation = relevel(Autocorrelation, "0"))

model_auto_trend <- glm(Agree ~ Autocorrelation * Trend,
                        family = binomial(link = "logit"),
                        data = VA)

summary(model_auto_trend)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_trend),
          confint.default(model_auto_trend, level = 0.95)))

writeLines("\n")

all_odds(model_auto_trend)
```

Here is variability with Trend, flipping variability.

```{r}
VA <- VA %>%
  mutate(Variability = relevel(Variability, "0.1"))

model_trend_var <- glm(Agree ~ Trend * Variability,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_var)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_var),
          confint.default(model_trend_var, level = 0.95)))
writeLines("\n")

all_odds(model_trend_var)
```

Here is the number of points in Phase A with trend.

```{r}

model_trend_A <- glm(Agree ~ Trend * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_A),
          confint.default(model_trend_A, level = 0.95)))
writeLines("\n")

all_odds(model_trend_A)
```

Here is the number of points in Phase B with trend.

```{r}

model_trend_B <- glm(Agree ~ Trend * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_B),
          confint.default(model_trend_B, level = 0.95)))
writeLines("\n")

all_odds(model_trend_B)
```

Here is effect size with trend.

```{r}
model_trend_es <- glm(Agree ~ Trend * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_es),
          confint.default(model_trend_es, level = 0.95)))
writeLines("\n")

all_odds(model_trend_es)
```

Now the forest plot.

```{r}
plot_data <- data.frame(
  Index = 1:5,
  label = c("Autocorrelation (0.2 to none)",
            "Relative Variation of Points (0.25 to 0.1)",
            "Baseline Number of Points (5 to 3)",
            "Intervention Number of Points (10 to 5)",            
            "Effect Size (moderate vs none or high)"),
  OR = c(1.16, 1.01, 1.07, 1.06, 1.31),
  LL = c(0.63, 0.55, 0.58, 0.57, 0.70),
  UL = c(2.16, 1.89, 1.99, 1.96, 2.46),
  CI = c("0.63, 2.16", "0.55, 1.89", "0.58, 1.99", "0.57, 1.96", "0.70, 2.46")
)

f_plot <- ggplot(plot_data, aes(y = Index, x = OR)) +
  geom_point(shape = 18, size = 5) +  
  geom_errorbarh(aes(xmin = LL, xmax = UL), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) +
  scale_y_continuous(name = "", breaks=1:5, labels = plot_data$label, trans = "reverse") +
  xlab("Ratio of Odds Ratios (95% CI)") + 
  ylab(" ") + 
  theme_bw() +
  theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.text.x.bottom = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black"))

table_base <- ggplot(plot_data, aes(y=label)) +
  ylab(NULL) + xlab("  ") + 
  theme(plot.title = element_text(hjust = 0.5, size=12), 
        axis.text.x = element_text(color="white", hjust = -3, size = 25),
        axis.line = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(),
        axis.title.y = element_blank(), 
        legend.position = "none",
        panel.background = element_blank(), 
        panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        plot.background = element_blank())

tab1 <- table_base + 
  labs(title = "space") +
  geom_text(aes(y = rev(Index),
                x = 1,
                label = sprintf("%0.2f", round(OR, digits = 2))), size = 4) +
  ggtitle("ROR")

tab2 <- table_base +
  geom_text(aes(y = rev(Index), x = 1, label = CI), size = 4) + 
  ggtitle("95% CI")

lay <-  matrix(c(1,1,1,1,1,1,1,1,1,1,2,3,3), nrow = 1)

grid.arrange(f_plot, tab1, tab2, layout_matrix = lay)
```

## Forest plot for effect interaction

First, here is autocorrelation with effect size, flipping autocorrelation.

```{r}
VA <- VA %>%
  mutate(Autocorrelation = relevel(Autocorrelation, "0.2"))

model_auto_effect <- glm(Agree ~ Autocorrelation * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_effect)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_effect),
          confint.default(model_auto_effect, level = 0.95)))
writeLines("\n")

all_odds(model_auto_effect)
```

The influence of effect size is greater when the autocorrelation is 0 than when it is 0.2, but this is not large and/or stable enough to infer with confidence (p = 0.27).

Now relative variation of points.

```{r}

model_var_es <- glm(Agree ~ Variability * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_es),
          confint.default(model_var_es, level = 0.95)))
writeLines("\n")

all_odds(model_var_es)
```

The influence of effect size on agreement is higher when the points have variability of 0.25 than when it is 0.1.

Now the interaction of number of points at baseline with effect size.

```{r}

VA <- VA %>%
  mutate(PointsA = relevel(PointsA, "5"))

model_A_es <- glm(Agree ~ PointsA * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_A_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_A_es),
          confint.default(model_A_es, level = 0.95)))
writeLines("\n")

all_odds(model_A_es)
```

Effect size is more influential with 3 points than with 5 at baseline.

Now number of points in intervention phase.

```{r}

VA <- VA %>%
  mutate(PointsB = relevel(PointsB, "10"))

model_B_es <- glm(Agree ~ PointsB * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_B_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_B_es),
          confint.default(model_B_es, level = 0.95)))
writeLines("\n")

all_odds(model_B_es)
```

Effect size has more influence with 5 points than with 10 at intervention phase.

Next interaction with trend.

```{r}
model_trend_es <- glm(Agree ~ Trend * ES_Factor,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_trend_es)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_trend_es),
          confint.default(model_trend_es, level = 0.95)))
writeLines("\n")

all_odds(model_trend_es)
```

Now the forest plot.

```{r}
plot_data <- data.frame(
  Index = 1:5,
  label = c("Autocorrelation (0 to 0.2)",
            "Trend (0 to 30 degree rotation)",
            "Relative Variation of Points (0.25 to 0.1)",
            "Baseline Number of Points (3 to 5)",
            "Intervention Number of Points (5 to 10)"),            
  OR = c(1.41, 1.31, 1.15, 1.11, 1.12),
  LL = c(0.77, 0.70, 0.63, 0.60, 0.61),
  UL = c(2.58, 2.46, 2.11, 2.02, 2.05),
  CI = c("0.77, 2.58", "0.70, 2.46", "0.63, 2.11", "0.60, 2.02", "0.61, 2.05")
)

f_plot <- ggplot(plot_data, aes(y = Index, x = OR)) +
  geom_point(shape = 18, size = 5) +  
  geom_errorbarh(aes(xmin = LL, xmax = UL), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) +
  scale_y_continuous(name = "", breaks=1:5, labels = plot_data$label, trans = "reverse") +
  xlab("Ratio of Odds Ratios (95% CI)") + 
  ylab(" ") + 
  theme_bw() +
  theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.text.x.bottom = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black"))

table_base <- ggplot(plot_data, aes(y=label)) +
  ylab(NULL) + xlab("  ") + 
  theme(plot.title = element_text(hjust = 0.5, size=12), 
        axis.text.x = element_text(color="white", hjust = -3, size = 25),
        axis.line = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(),
        axis.title.y = element_blank(), 
        legend.position = "none",
        panel.background = element_blank(), 
        panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        plot.background = element_blank())

tab1 <- table_base + 
  labs(title = "space") +
  geom_text(aes(y = rev(Index),
                x = 1,
                label = sprintf("%0.2f", round(OR, digits = 2))), size = 4) +
  ggtitle("ROR")

tab2 <- table_base +
  geom_text(aes(y = rev(Index), x = 1, label = CI), size = 4) + 
  ggtitle("95% CI")

lay <-  matrix(c(1,1,1,1,1,1,1,1,1,1,2,3,3), nrow = 1)

grid.arrange(f_plot, tab1, tab2, layout_matrix = lay)
```

## Forest plot for other interactions

Next we will look at whether *autocorrelation* and *variability* interact when influencing expert agreement.

```{r}

model_auto_var <- glm(Agree ~ Autocorrelation * Variability,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_var)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_var),
          confint.default(model_auto_var, level = 0.95)))

writeLines("\n")

all_odds(model_auto_var)
```

A change in the variability of the points does not make much difference in the odds ratio for autocorrelation.

Next we will look at whether *autocorrelation* and *number of points in Phase A* interact when influencing expert agreement.

```{r}

model_auto_A <- glm(Agree ~ Autocorrelation * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_A),
          confint.default(model_auto_A, level = 0.95)))

writeLines("\n")

all_odds(model_auto_A)
```

A change in the number of the points in Phase A does not make much difference in the odds ratio for autocorrelation.

Next we will look at whether *autocorrelation* and *number of points in Phase B* interact when influencing expert agreement.

```{r}

VA <- VA %>%
  mutate(Autocorrelation = relevel(Autocorrelation, "0"))

model_auto_B <- glm(Agree ~ Autocorrelation * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_auto_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_auto_B),
          confint.default(model_auto_B, level = 0.95)))

writeLines("\n")
all_odds(model_auto_B)
```

A change in the number of points in Phase B does not make much difference in the odds ratio for autocorrelation.

Next we will look at whether *variability* and *number of points in Phase A* interact when influencing expert agreement.

```{r}

model_var_A <- glm(Agree ~ Variability * PointsA,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_A)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_A),
          confint.default(model_var_A, level = 0.95)))

writeLines("\n")
all_odds(model_var_A)
```

Next we will look at whether *variability* and the *number of points in Phase B* interact when influencing expert agreement.

```{r}

VA <- VA %>%
  mutate(Variability = relevel(Variability, "0.25"))

model_var_B <- glm(Agree ~ Variability * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_var_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_var_B),
          confint.default(model_var_B, level = 0.95)))

writeLines("\n")
all_odds(model_var_B)
```

Next we will look at whether the *number of points in Phase A* and the *number of points in Phase B* interact when influencing expert agreement.

```{r}
VA <- VA %>%
  mutate(PointsA = relevel(PointsA, "3"))

model_A_B <- glm(Agree ~ PointsA * PointsB,
                      family = binomial(link = "logit"),
                      data = VA)

summary(model_A_B)
writeLines("\n")

exp(cbind("Odds ratio" = coef(model_A_B),
          confint.default(model_A_B, level = 0.95)))

writeLines("\n")
all_odds(model_A_B)
```

The odds ratio for the number of points in Phase A is a little higher when there are five points in Phase B than when there are ten points in Phase B, but this estimate is not stable enough to infer these results with high confidence.

Now the forest plot.

```{r}
plot_data <- data.frame(
  Index = 1:6,
  label = c("Autocorrelation & Variability",
            "Autocorrelation & Baseline Number of Points",
            "Autocorrelation & Intervention Number of Points",
            "Variability & Baseline Number of Points",
            "Variability & Intervention Number of Points",
            "Baseline & Intervention Number of Points"),            
  OR = c(1.26, 1.20, 1.23, 1.62, 1.12, 1.41),
  LL = c(0.69, 0.66, 0.68, 0.89, 0.61, 0.78),
  UL = c(2.30, 2.18, 2.22, 2.95, 2.03, 2.56),
  CI = c("0.69, 2.30", "0.66, 2.18", "0.68, 2.22", "0.89, 2.95", "0.61, 2.03",
         "0.78, 2.56")
)

f_plot <- ggplot(plot_data, aes(y = Index, x = OR)) +
  geom_point(shape = 18, size = 5) +  
  geom_errorbarh(aes(xmin = LL, xmax = UL), height = 0.25) +
  geom_vline(xintercept = 1, color = "red", linetype = "dashed", cex = 1, alpha = 0.5) +
  scale_y_continuous(name = "", breaks=1:6, labels = plot_data$label, trans = "reverse") +
  xlab("Ratio of Odds Ratios (95% CI)") + 
  ylab(" ") + 
  theme_bw() +
  theme(panel.border = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.text.x.bottom = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black"))

table_base <- ggplot(plot_data, aes(y=label)) +
  ylab(NULL) + xlab("  ") + 
  theme(plot.title = element_text(hjust = 0.5, size=12), 
        axis.text.x = element_text(color="white", hjust = -3, size = 25),
        axis.line = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks = element_blank(),
        axis.title.y = element_blank(), 
        legend.position = "none",
        panel.background = element_blank(), 
        panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        plot.background = element_blank())

tab1 <- table_base + 
  labs(title = "space") +
  geom_text(aes(y = rev(Index),
                x = 1,
                label = sprintf("%0.2f", round(OR, digits = 2))), size = 4) +
  ggtitle("ROR")

tab2 <- table_base +
  geom_text(aes(y = rev(Index), x = 1, label = CI), size = 4) + 
  ggtitle("95% CI")

lay <-  matrix(c(1,1,1,1,1,1,1,1,1,1,2,3,3), nrow = 1)

grid.arrange(f_plot, tab1, tab2, layout_matrix = lay)
```
